---
title: "Package 'cleanIGRA' Vignettes"
author: "Jackson Kwok"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{main_functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
###Key functionality 
There is only one key function in this package: ```clean_IGRA```. It parses the raw data and converts them into R dataframe. See usage below. 

```{r, results = 'hide', cache = TRUE}
library(cleanIGRA)
filepath <- system.file("extdata//", "89002.y2d", package = "cleanIGRA")
mydata <- clean_IGRA(filepath, type = 'file')  #key function
```
```{r}
DT::datatable(head(mydata, 100), options = list(scrollX = TRUE,  pageLength = 5))  #show results
```

###Add-ons functionality
The following are some 'add-ons' facilities:  

1. ```fix_data_type``` converts some of the measurement variables from characters strings to numeric values and labels missing data (marked as -8888 and -9999) as NA. It also corrects the scale of the data. See "IGRA readme file" for more details. 
2. ```group_by_level``` splits the dataframe into a list of dataframes according to the pressure level.  
3. ```aggregate_temperature_by_month``` aggregates daily temperature measurement to monthly measurement. It uses simple averaging by default.  

```{r}
library(magrittr)
mydata_level_list <- mydata %>% fix_data_type() %>% group_by_level()
mydata_first_level <- mydata_level_list[[1]]
mydata_monthly <- aggregate_temperature_by_month(mydata_first_level)  #convert the 1st level to monthly data
```
```{r}
mydata_monthly$temp %<>% round(1)  #rounding for display purposes
DT::datatable(mydata_monthly, options = list(scrollX = TRUE, pageLength = 5))  #show results
```
